### 2015-02-12 paper_10_intro.tex
adding a reference
minor updates

    One of the software analytic techniques focuses specifically 
    on the source code; analyzing the 
    complexity, size, and coupling \cite{Tosi2012}. 
    Letier and Fitzgerald discuss how to choose the 
    correct tools and techniques to analyze
    software data \cite{Letier2013}.  A goal model is 
    produced that matches the data analysis methods
    with the goals of the software stakeholders. The method does not focus
    specifically on analysis of the development of software.

@@

    So it has been shown, there exist many attempts to 
    evaluate portions of the a software development 
    organization.  None of the the attempts provide
    a single number score for the entirety of the 
    organization.  Most of the techniques focus on
    specific portions of the software development 
    lifecycle, namely the development portion. Plus,
    there are many tools that need to be created for
    software analytics to provide all the value
    that it promises.

>>>>

    Lavazza, Morasca, Taibi, and Tosi focus specifically 
    on the source code; analyzing the 
    complexity, size, and coupling \cite{Tosi2012}. 
    They created a theoretical framework
    for dynamic measurements instead of traditional static measures.
    Letier and Fitzgerald discuss how to choose the 
    correct tools and techniques to analyze
    software data \cite{Letier2013}.  A goal model is 
    produced that matches the data analysis methods
    with the goals of the software stakeholders. The method does not focus
    specifically on analysis of the development of software.

@@

    Overall, there exist many attempts to 
    evaluate portions of the a software development 
    organization.  None of the the attempts provide
    a single number score for the entirety of the 
    organization.  Most of the techniques focus on
    specific portions of the software development 
    lifecycle, namely the development portion. Plus,
    there are many tools that need to be created for
    software analytics to provide all the value
    that it promises.
